### 2025-01-11 manuscript/manuscript.tex
update refs

>>>>

SOM and landscape \parencite{doetterl2025a-landscape-scale}

\section{Bibliometrics}

Crossref and Dimensions compare with Google Scholar, Microsoft Academic, Scopus and the Web of Science? \parencite{harzing2019two-new-kids}

Ecosystem data integration is incorporating the available knowledge at the system level.
This type of integration is needed to decipher ecosystem function.

Crete has been sampled for soil and biodiversity in many different ecosystems.

These data were coupled with open data about Crete island that fall in literature,
samplings and maps categories. The literature analysis showed the huge catalogue of historical datasets are not still incorporated in open databases.
Regarding maps, there are different aspects of the soil ecosystem, climate,
geology, elevation and slope, soil type, land cover type, land management are
among the major aspects of the Crete Soil System. In addition, Crete has been
assessed for climate change and desertification in many studies adding more
layers of information to create a Crete Soil System. All these data are further establishing Crete as a great soil model island.

Socio ecological \parencite{balzan2019improving}.
